%\documentclass[prd,amsmath,amssymb,floatfix,nofootinbib,preprintnumbers,twocolumn]{revtex4}%showpacs,superscriptaddress
%\documentclass[prd,amsmath,amssymb,floatfix,nofootinbib,preprintnumbers]{revtex4}%showpacs,superscriptaddress
\documentclass[a4paper,11pt]{article}
\usepackage{jcappub}

\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{hyperref}
\hypersetup{colorlinks=True,citecolor=blue}
\usepackage{amssymb}
\usepackage{graphicx,multirow}
\usepackage{subfigure}
%\usepackage{soul}
\usepackage[normalem]{ulem}

\renewcommand*{\thesubfigure}{(\roman{subfigure})}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

%\usepackage{caption}
%\usepackage{float}
%\usepackage{bm}
%\usepackage{latexsym}
%\usepackage{epsfig}
%\usepackage{graphicx,color}
\usepackage{bbold}
%\usepackage{caption}
%\usepackage{subcaption}


\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqry}{\begin{eqnarray}}
\newcommand{\eeqry}{\end{eqnarray}}
\newcommand{\beqrys}{\begin{subequations}\begin{eqnarray}}
\newcommand{\eeqrys}{\end{eqnarray}\end{subequations}}

\newcommand{\fqu}{\begin{bmatrix} Q \\ U \end{bmatrix}}
\newcommand{\xpm}{\begin{bmatrix} _{+2}X \\ _{-2}X \end{bmatrix}}
\newcommand{\equ}{\begin{bmatrix} Q \\ U \end{bmatrix}_{E}}
\newcommand{\bqu}{\begin{bmatrix} Q \\ U \end{bmatrix}_{B}}
\newcommand{\eblm}{\begin{bmatrix} a^E \\ a^{B} \end{bmatrix}}
\newcommand{\qutox}{\begin{bmatrix} \mathbb{1} & i\mathbb{1}  \\  \mathbb{1} & -i\mathbb{1}   \end{bmatrix}}
\newcommand{\qutoxd}{\begin{bmatrix} \mathbb{1} & \mathbb{1}  \\  -i\mathbb{1} & i\mathbb{1}   \end{bmatrix}}
\newcommand{\ymat}{\begin{bmatrix} _{+2}Y & 0  \\  0 & _{-2}Y  \end{bmatrix}}
\newcommand{\ymatc}{\begin{bmatrix} _{+2}Y^* & 0  \\  0 & _{-2}Y^*  \end{bmatrix}}
\newcommand{\yzmat}{\begin{bmatrix} _{0}Y & 0  \\  0 & _{0}Y  \end{bmatrix}}
\newcommand{\yzmatc}{\begin{bmatrix} _{0}Y^* & 0  \\  0 & _{0}Y^*  \end{bmatrix}}
\newcommand{\ope}{\hat{O}_{E}}
\newcommand{\opb}{\hat{O}_{B}}
\newcommand{\bmat}{\begin{bmatrix}}
\newcommand{\emat}{\end{bmatrix}}

\def\vp#1{$\bar{P}_{#1}$ }
\def\vs{$\bar{S}~$}

\newcommand{\st}{\sout}
\newcommand{\revisit}{\textcolor{red}}
\newcommand{\comment}{ $\Rightarrow$ \textcolor{green}  }
\newcommand{\rfedit}{\textcolor{magenta}  }
\newcommand{\soothe}{\textcolor{BlueViolet}  }

\def\eq#1{{Eq.~(\ref{#1})}}
\def\sec#1{{Sec.~\ref{#1}}}
\def\fig#1{{Fig.~\ref{#1}}}
\def\app#1{{Appendix~\ref{#1}}}
\def\ymat#1{\begin{bmatrix} _{+2}Y_{#1} & 0  \\  0 & _{-2}Y_{#1}  \end{bmatrix}}
\def\ymatc#1{\begin{bmatrix} _{+2}Y^{T*}_{#1} & 0  \\  0 & _{-2}Y^{T*}_{#1}  \end{bmatrix}}
\def\yzmat#1{\begin{bmatrix} _{0}Y_{#1} & 0  \\  0 & _{0}Y_{#1}  \end{bmatrix}}
\def\yzmatc#1{\begin{bmatrix} _{0}Y^*_{#1} & 0  \\  0 & _{0}Y^*_{#1}  \end{bmatrix}}


\graphicspath{ {"../../figures/"//} }

\begin{document}

\title{Local real space operators for translating Stokes Q/U to E/B maps on the sphere }
\author[]{Aditya Rotti and}
\author[]{Kevin Huffenberger}
\affiliation[]{Department of Physics, Florida State University, Keen Physics Building, 77 Chieftan Way, Tallahassee, Florida, U.S.A.}
\emailAdd{adityarotti@gmail.com}
\emailAdd{khuffenberger@fsu.edu}

\abstract{
\noindent We derive real space operators to translate Stokes Q/U to coordinate independent even and odd parity E/B fields on the sphere and demonstrate their numerical equivalence to the harmonic space methods. In process we also derive real space operators which allow direct decomposition of measured Q/U into Q/U fields corresponding to E-modes and B-modes respectively. These operators are derived on the sphere and account for the curvature effects. The analytical derivations reveal a functional form for the radial kernel, which quantifies the non-local nature of the E and B fields. 
%and their dependence on the band limit of the measurement. 
These real space operators allow the computation of E and B field in each pixel by integrating in a small region around it, and hence it can be easily parallelized and is not memory intensive. A major drawback of these real space operators is that they cannot reliably construct modes on large angular scales $\ell<50$ with ease. Finally, this study motivates the construction of more locally defined E and B maps, by making desired alterations to the radial filter. We demonstrate that these altered E mode and B mode constructions do not significantly distort spectral information on small angular scales. %Such locally constructed E and B maps may help mitigate the foreground leakage issue across the two modes.
}

\maketitle

\include{./sections/introduction}
\include{./sections/real_space_formalism}
\include{./sections/kernel_discussion}
\include{./sections/generalizedeb}
\include{./sections/numerical_implementation}
\include{./sections/application_353ghz}
\include{./sections/discussion}
\include{./sections/appendix}

\bibliographystyle{JHEP}
\bibliography{ref}

\end{document}